---
title: "ReproHack NL, 2019"
output:
    html_document:
        theme: flatly
        css: reprohack.css
params: 
  title: "Leiden University"
  room_location: "Leiden University Library"
  address: "Witte Singel 27, 2311 BG Leiden"
  date: "30th November, 2019"
  time: "10 am - 5pm"
  bannerurl: "reprohack-banner.png"
  latitude: 52.157305
  longitude: 4.481427
  registration_url: https://www.eventbrite.co.uk/e/reprohack-nl-tickets-73258469053
  submission_url: https://docs.google.com/forms/d/1BwCNsO5FFp_n9eYJJcujmQ1YdJKYp-5gIqL4zH0u3H8/edit
  reprohack_repo_url: https://github.com/ReproHackNL/ReproHack
---
```{r, include=FALSE}
twit_icon <- icon:: fa("twitter", colour = "#09754a")
```

```{r, echo=FALSE}
openstreetmaps_location_url <- paste0("https://www.openstreetmap.org/?mlat=",
                                      params$latitude,
                                      "&mlon=", params$longitude,
                                      "#map=19/", params$latitude, "/",
                                      params$longitude)
```
![](`r params$bannerurl`)

# **ReproHack @ `r params$title`**
## _A hands-on Reproducibility Hackathon_

<br>

***

##### &#x1F4C5; `r params$date`
##### &#x23F0; `r params$time`
##### &#x1F4CD; `r params$room_location`
##### &#x1F5FA;&#xFE0F; [**`r params$address`**](`r openstreetmaps_location_url`)

***

## Welcome &#x1F44B; {.tabset .tabset-fade}

### **What's a ReproHack?** 

We are all excited by the progress made by many authors to **make their papers reproducible by publishing associated code and data**. 

We know how challenging it can be so we **want to showcase the value of the practice**, both for original authors and as a learning experience for those who attempt to reproduce the work.

During a **ReproHack**, participants attempt to reproduce published research of their choice from a list of _proposed papers with publicly available associated code and data_. Participants get to work with other people’s material in a low pressure environment and record their experiences on a number of key aspects, including **reproducibility, transparency and reusability of materials**. At the end of the day we regroup, share our experiences and give feedback to the authors.

<br>

_It's imperative to note that  **ReproHacks are by no means an attempt to criticise or discredit work**. We see reproduction as **beneficial scientific activity in itself**, with useful outcomes for authors and valuable learning experiences for the participants and the research community as a whole._

_We strive to make this event open and inclusive to all. As such we ask you to read our [Code of Conduct](https://docs.carpentries.org/topic_folders/policies/code-of-conduct.html). By participating, you are expected to uphold this code._

<br>

### **Join the event and reproduce &#x267B;&#xFE0F;**

##### Register and save your spot by clicking [here](https://www.eventbrite.co.uk/e/reprohack-nl-tickets-73258469053)!


_Join us at the ReproHack and get working with other people’s material._

###### Benefits to participants:

- Practical experience in reproducibility with real published materials and the opportunity to explore different tools and strategies.

- Inspiration from working with other people’s code and data.

- An appreciation that reproducibility is non trivial but that opening up your work for more people to engage with is the best way to help improve it.
An appreciation that reproducibility has community value beyond just the validation of the results. For example, access to such materials increases the potential for reuse and understanding of the work.

###### Benefits to the whole research community:

- Assessment of how reproducible papers are ‘out of the box’.

- Evaluation of how successful current practices are and for what purpose.

- Identification of what works and where the most pressing weaknesses in our approaches are.

<br>

<br>

```{r, echo=FALSE, warning=FALSE}
library("shiny")
 wellPanel(a("Register", class = "btn btn-primary btn-md",
          href = params$registration_url))
```


<br>

### **Propose a paper &#x1F4DC;**

##### Click [here](https://docs.google.com/forms/d/1BwCNsO5FFp_n9eYJJcujmQ1YdJKYp-5gIqL4zH0u3H8/edit) to nominate your paper!

_You've put a lot of effort into making your work reproducible. Now let people learn from and engage with it!_

We invite nominations for papers that have both associated **code** and **data** publicly available. We also encourage analyses based on open source tools as we cannot guarantee participants will have access to specialised licenced software.

<br>

###### Benefits to authors:

- **Feedback** on the reproducibility of your work.

- **Appreciation** for your efforts in making your work reproducible.

- Opportunity to **engage others with your research**.

<br>

```{r, echo=FALSE}
library("shiny")
 wellPanel(a("Nominate Paper", class = "btn btn-primary btn-md",
          href = params$submission_url))
```

###### **Proposed papers:**

<br>

```{r, echo=FALSE, message=FALSE, warning=FALSE, eval=require('googlesheets')}
library(googlesheets)
library(dplyr)
```

```{r, echo=FALSE}
print_contact_links <- function(responses, i){
  row <- responses[i, ]
  twitter <- if(!is.na(row[,"Twitter handle"])){
twitter_url <- paste0("https://twitter.com/", gsub(" *@ *", "", row[,"Twitter handle"]))
  paste0("[twitter](", twitter_url,")")}else{NULL}

  github <- if(!is.na(row[,"GitHub username (to open issues on GitHub if needed)"])){
  github_url <- paste0("https://github.com/", gsub(" *@ *", "", row[,"GitHub username (to open issues on GitHub if needed)"]))
  paste0("[github]('github_url')")}else{NULL}

  feedback <- if(row[, "Would you like to receive a copy of any feedback on the paper?"] == "Yes"){
    "<i class='fa fa-comment-dots'/>"}else{NULL}
  public <- if(row[,"Can feedback on your paper be made public?"] == "Yes"){
    "<i class='fa fa-globe'/>"}else{NULL}

  return(paste(twitter,github, feedback, public))
}
```

```{r, message=FALSE, results='asis', warning=FALSE,  echo=FALSE}
library(lubridate)
responses_gs <- gs_title("ReproHackNL: Propose a paper to reproduce (Responses)")
responses <- gs_read(responses_gs)

responses <- responses %>% 
  arrange(Timestamp)

if(nrow(responses) > 0){

for(i in 1:nrow(responses)){
    cat('\n')
    cat('\n')
    cat('\n')
    cat("###### **", i,". ", as.character(responses[i, "Paper title"]), "**", "\n", "\n", sep = "")
    cat("**", gsub("\n", "", gsub("[*]", "", as.character(responses[i, "Paper citation"]))), "\n**", "\n", "\n", sep = "")
    cat("####### *submitted by ", as.character(responses[i, "Name"]),  print_contact_links(responses, i), "*", "\n")
    cat('\n')
    cat('\n')
    cat("**Why should we attempt to reproduce this paper?**", "\n", "\n")
    cat(as.character(responses[i, "Why should we attempt to reproduce this paper?"]), "\n")
    cat('\n')
    cat("**Paper URL:** [", as.character(responses[i, "Paper URL"]),"](",as.character(responses[i, "Paper URL"]) ,")", "\n")
    cat('\n')
    cat("**Data URL:**", as.character(responses[i, "Data URL"]), "\n")
    cat('\n')
    cat("**Code URL:**", as.character(responses[i, "Code URL"]), "\n")
    cat('\n', "\n")
    cat("**Useful programming skills:**", as.character(responses[i, "Useful programming skills"]), "\n")
    cat('\n', "\n",'\n')
}

}
```


<br>


### **Program &#x1F4C5;**

10:00 Coffee and Tea &#x2615;

10:30 Welcome

10:40 "Reproducibility: The value in the practice" by [Dr. Anna Krystalli](http://www.annakrystalli.com/)

11:30 Forming groups and start hackathon &#x1F468;&#x1F3FB;&#x200D;&#x1F4BB;
&#x1F468;&#x1F3FC;&#x200D;&#x1F4BB;

12:30 Lunch buffet &#x1F957; &#x1F959;

14:30 "A vision for Open Science beyond the reproducibility crisis" by [Dr. John Boy](https://www.jboy.space/)

15:00 Continue hacking &#x1F468;&#x1F3FD;&#x200D;&#x1F4BB;&#x1F469;&#x1F3FC;&#x200D;&#x1F4BB;




16:30 Drinks and bites &#x1F37B;


<br>

### **Feedback form**

Please fill this [feedback form](https://forms.gle/Qprt2cCpoeQPSwhZ7) after you reproduced the paper that you picked! 

We want to emphasize that we appreciate all authors who have nominated their papers for the hackathon, and so we expect that any feedback and criticism on authors’ work is expressed in a *constructive*, friendly and respectful manner. 

## **Find us:**

`r icon:: fa("paper-plane", colour ="#09754a")` reprohack.nl@gmail.com
<br>
`r icon:: fa("twitter", colour ="#09754a")`https://twitter.com/ReproHackNL

